Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Joining the positive diagnosis for depression and anxiety by sample

dat.retro_mdd_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise(mdd_total = n())

@@

>>>>

dat.retro_mdd_by_sample <- dat.retro_mdd_by_sample %>% 
  group_by(Sample_plot) %>% 
  summarise(mdd_total = n())

@@

```{r Merge the positive sample/diagnosis tibbles}

dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_mdd_by_sample,
                                                    dat.retro_anxi_by_sample,
                                                    by = "Sample_plot")

head(dat.retro_positive_diagnosis_by_sample)
